\begin{thebibliography}{100}
\bibitem[1]{Benchmarking1}Christian Beckel,Leyna Sadamori and Silvia Santini, "\emph{Towards Automatic Classification of Private Households -Using Electricity Consumption Data}", Buildsys’12, November 6, 2012, Toronto.
\bibitem[2]{faultdetec1} Joern Ploennigs, Bei Chen, Anika Schumann and Niall Brady, "\emph{Exploiting Generalized Additive Models for Diagnosing Abnormal Energy Use in Buildings}", Buildsys’13, November 13-14-2013, Roma, Italy.

\bibitem[3]{faultdetec2}Xiaoli Li, Chris P. Bowers, and Thorsten Schnier, "\emph{Classification of Energy Consumption in Buildings With Outlier Detection}", IEEE TRANSACTIONS ON INDUSTRIAL ELECTRONICS, Vol. 57, No. 11, November, 2010.

\bibitem[4]{faultdetec3}Imran Khana, Alfonso Capozzolia, Stefano Paolo Corgnatia and Tania Cerquitellib, "\emph{Fault Detection Analysis of Building Energy Consumption -Using Data Mining Techniques}", Elsevier Ltd, 2013.

\bibitem[5]{faultdetec4}John E. Seem, "\emph{Pattern recognition algorithm for determining days of the week with similar energy consumption profiles}", Elsevier B.V, 2004.


\bibitem[6]{OutDetec1}Peter Filzmosera Ricardo Maronnab, MarkWernerc, "\emph{Outlier identification in high dimensions}", Elsevier B.V., 2007
\bibitem[7]{Benchmarking2} Teemu Räsänen, Juhani Ruuskanen and Mikko Kolehmainen, "\emph{Reducing energy consumption by using self-organizing maps to create more personalized electricity use information}", Elsevier Ltd., 2008

\bibitem[8]{PeterJRousseeuw}Peter J. Rousseeuw (1987). "\emph{Silhouettes: a Graphical Aid to the Interpretation and Validation of Cluster Analysis}". Computational and Applied Mathematics 20: 53–65

\bibitem[9]{interaction}Yvonne Rogers, Helen Sharp and Jennifer Preece, "\emph{Interaction Design, -beyound human-computer interaction}", Wiley, 3rd Edition, 2012

\end{thebibliography}
